% main.tex
%
% Root of the document tree. Includes the abstract and notes.
\documentclass[letter]{article}
\usepackage{color,soul}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\input{header.tex}
\input{macros.tex}

\date{\today}
\title{\textbf{Verifiable DPF Schemes}}
\author{Christopher Patton}

\setcounter{tocdepth}{2}

\begin{document}

\maketitle

\begin{abstract}
  The point function of binary strings~$X$ and~ $Y$ is defined by $P_{X,Y}(X) =
  Y$ and $P_{X,Y}(X^\prime) = 0^{|Y|}$ for all $X^\prime \ne X$. A distributed
  point function (DPF) scheme maps~$P_{X,Y}$ to a sequence of shares which, when
  combined, yield the point function, but from a subset of which neither~$X$
  nor~$Y$ can be recovered. This primitive was first suggested in the context of
  private information retrieval where the goal is to allow clients to \emph{read
  from} a database distributed among a set of servers without revealing which
  data were read. It was recently proposed as a way to address traffic analysis
  attacks in the context of anonymous communication.
  %
  The goal of the Riposte cryptosystem \cite{riposte} is to allow clients to
  \emph{write to} a distributed database without revealing to the servers which
  data were written. However, by sending the servers mal-formed shares, a
  malicious client or network adversary can easily corrupt the database state.
  As pointed out by the designers, it is crucial in this setting that the
  servers be able to verify their shares are correct. We endow DPF schemes with
  a property we call \emph{verifiability} and put forward a unified framework
  for their analysis, which yields more efficient verification protocols with
  stronger security properties.
\end{abstract}

\section{Introduction}
\input{intro.tex}

\section{Related work}
\input{related.tex}

\section{Preliminaries}
\input{prelims.tex}

\section{DPF schemes}
\input{dpf.tex}

\section{A $2$-server+auditor protocol}
\input{twowriter.tex}

\if{0}
\section{Riposte}
\input{riposte.tex}
\fi

\section{Notes}
\begin{itemize}
  \item Ilya Mironov (mironov@) suggests that the error correction coding could
    be done more efficient. In the paper, they consider coding schemes for
    general finite fields, but there are faster ways when you're working with
    fields with binary coefficients (i.e. $GF(2^n)$). Ananth (pseudorandom@)
    says to focus on arguing for distributed trust model from a privacy
    perspective.  Ulfar Erlingsson (ulfar@) argues that distributing trust is a
    means of keeping the data collector honest; in order to violate your
    privacy, they'd have to do it explicitly. It makes an insider attack much
    harder, avoids inadvertently linking collected data to client identity, and
    makes it so an outside attacker has two targets instead of one.


  \item ``Silent'' versus ``explicit'' collusion. I'll need to be rigorous about
    what it means to be a valid protocol message.

  \item Compare to mixnets: an active adversary controlling the entry mix can
    learn the message sent by client it wishes (all-but-one attack). Mounting
    this attack Riposte would require network control.

  \item Ulfar's straw man scheme: use a ``stock'' secret sharing scheme to map
    the message to $s$ shares. Generate a random nonce and append it to each of
    the shares. Send each string to one of the write servers. Once a write
    server has received $N$ shares, it outputs them to the auditor in a random
    order.  Once the auditor has received $N$ shares from each of the $s$ write
    servers, it combines the shares and outputs them in a random order to the
    data consumer. This protocol fails in two ways. First, one of the write
    servers could mount the all-but-one attack. (This can be overcome by
    having the clients encrypt their shares under the public key of the auditor
    or by making the messages ``self-authenticating'' as suggested by Ilya.)
    Second, it's possible for one of the write servers to silently collude with
    the auditor. By not shuffling, a write server communicates the order of
    arrival to the auditor.
\end{itemize}

\section{Acknowledgements}
\input{ack.tex}

\bibliography{main}
\bibliographystyle{plain}

\end{document}
