% dpf.tex
%
% Syntax, definitions, and applications of verifiable DPF schemes.

In this section, we give syntax and security notions for distributed point
functions. We diverge somewhat from the syntax of \cite{dpf} as it will be
convenient in our setting to assume the domain have algebraic
structure.\cpnote{Is this actually more convenient? Since our constructions are
mostly based on pseudorandom generators, it might make more sense to think of
the domain as strings. Yet there's the $\sharect$-server Riposte variant to
consider.}
Let~$\ring$ be a finite ring and let $\msgsp = \ring \setminus \{ 0 \}$
where~$0$ denotes the additive identity. Let $\dblen \in \N$, $\idx \in
[\dblen]$, and $\msg \in \msgsp$.
%
The \emph{point function} of $(\idx, \msg)$ is the map $P_{\idx,\msg} : [\dblen]
\to \ring$ where $P_{\idx,\msg}(\idx) = \msg$ and for every $\idx^\prime \ne
\idx$, it holds that $P_{\idx,\msg}(\idx^\prime) = 0$.
%
The notation~$\msgsp$ signifies that the set of non-zero elements of~$\ring$
constitutes a message space and that~$\msg$ encodes the message to be written
into the database. The value~$\idx$ indicates the row of the database to
which~$\msg$ is to be written.

We remark that the message space in the formalization of~\cite{riposte} is~$F
\setminus \{0\}$ where~$F$ is a finite field. Each element having a
multiplicative inverse is necessary in order to implement their error correcting
code for dealing with collisions in the table, but this extra structure is not
essential for formalizing the security properties of the scheme.\cpnote{Does the
seed-homomorphic PRG need field structure? I don't think so.}

Concretely, we may define a ring on $n$-bit strings as follows.  Addition of~$X$
and~$Y$ is defined by $X \xor Y$. The all-zero string~$0^n$ is then the additive
identity. To compute $Z = X\cdot Y$, we regard the $i$-th bit of~$X$ (resp.~$Y$)
as the $i$-th coefficient of a polynomial~$p_X(x)$ (resp.~$p_Y(x)$), compute the
polynomial~$p_Z(x)$ congruent to $p_X(x)\cdot p_Y(x) \mod x^{n+1}$, and
let~$Z[i]$ be the $i$-th coefficient of~$p_Z(x)$ for each $i \in
[n]$.

\subsection{Syntax}
\input{syntax.tex}

\subsection{Security}
\input{security.tex}

\subsection{Application to anonymous reporting}
\input{anon.tex}
