%
%
%
\renewcommand{\ng}{\schemefont{ng}}
\newcommand{\he}{\schemefont{he}}
\newcommand{\foobar}{\textsc{foobar}}
In their treatment of nonce-based, public-key
cryptography~\cite{bellare2016nonce}, Bellare and Tackmann introduce two notions
of secure encryption. \foobar!
%
The first, NBP1, extends the usual IND-CCA notion to a new setting in which
encryption is determinsitc and takes as input the public key~$\pk$ and
message~$m$, as well as a nonce~$n$ and an input~$\xk$, called the \emph{seed},
known only to the sender. Decryption has the usual syntax; it requires only the
ciphertext and secret key. The nonce~$n$ is output by a stateful (and possibly
randomized) procedure~$\ng$, called the \emph{nonce generator}. This algorithm
takes as input a string~$\sel$, called the \emph{nonce selector}. In the NBP1
setting we assume that, at a minimum, the pair $(m, \sel)$ does not repeat.
%
The second notion, NBP2, models the setting where the sender's state is
(partially) exposed to the adversary. The primary distinction between NBP1 and
NBP2 is that, in the latter, the adversary is given~$\xk$ as input. As a result,
ensuring that $(m, \sel)$ not repeat is not enough for security; the output
of~$\ng$ must also be \emph{unpredictable} to the adversary.

Their main construction involves a novel primitive~$\he$, called a \emph{hedged
extractor}. It takes as input the seed, the message~$m$, and the nonce~$n$, and
outputs a string~$r$. This string is used as the coins for encryption of~$m$
using a standard PKE scheme. This composition achieves NBP1 if~$\he$ is a PRF,
and it achieves NBP2 if~$\he$ is secure in a new sense
that~\cite{bellare2016nonce} defines.
%
Roughly speaking, this RoR (``real-or-random'') notion ensures that, if the
output of~$\ng$ is unpredictable, then the output of~$\he$ is indistinguishable
from a random string, even to an adversary in possession of the seed.

Interestingly, the composition of~$\he$ and~$\ng$ is remarkably similar to how
pseudo random number generation works in real systems. PRNGs \emph{with input},
first formalized by Barak and Halevi~\cite{barak2005model}, typically have two
interfaces: one that fetches (any number of) pseudorandom bits, and another with
which the programmer can provide additional randomness to the PRNG state. A number
of notions of security have been considered for this primitive, including some
that model exposure of the state to the adversary. The motivation for these
notions is not dissimilar to that of the RoR game described above.

\cptodo{Segway}
%
In the NBP2 game, the adversary is given the seed as input, but the state
associated with nonce generation remains hidden. In my opinion, this setting is
not clearly motivated; an adversary that is able to penetrate the sender's
system and exfiltrate the seed ought to be able to recover the~$\ng$ state.
%
Of course, secure encryption \emph{after} this state is exposed is impossible, a
limitation that~\cite{bellare2016nonce} recognizes: in the RoR game for hedged
extractors, the adversary is given access to the~$\ng$ state, but only
\emph{after} it makes its queries. Said another way, RoR security for hedged
extractors is only guaranteed for coins generated prior to state exposure.

In this work, we reconsider the adversarial model described by NBP2, opting for
a simpler notion in which the encryption state is exposed to the adversary after
it makes its encryption queries.
%
We consolidate the stateless, deterministic encryption algorithm
and the stateful nonce generator into one stateful, deterministic encryption
procedure. We do away with the seed and instead define stateful, pseudorandom
number generation as a primitive for constructing such a scheme.

Finally, our syntax and security notions are geared towards the application of
password-based authenticated key exchange. In this direction, our syntax admits
a nonce and associated data, which may be used as the session number and
password respectively.

\cptodo{Talk about why decryption should take the nonce as input. (In
\cite{bellare2016nonce}, the nonce is used only to ensure coins freshness.)}
